---
title       : Apartment Price Predictor
subtitle    : Developing Data Products Course Project
author      : Matti Pekari
job         : 
framework   : io2012       # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Introduction

* Investing in real estate requires estimating realistic prices
* Market prices for real estate depend on a large number of factors
* The estimation process can be automated using machine learning techniques
* Estimate provided by the model can be used as a baseline for own estimate

--- 

## How to use the app

* Apartment Price Predictor is an app that estimates the sales price of an apartment based on inputs provided by the user
* The user can define several attributes for the apartment, such as location, size, year built and condition
* The app sends the provided input attributes to a predictive model on the server side
* The predicted price provided by the model is sent back and printed on the UI

--- 

## How does the predictive model work

* The predictive model was trained using actual apartment sales prices in Helsinki, Finland in 2013
* The sales prices are publicly available on a website provided by the government
* The training set consisted on approx. 4500 observations
* The algorithm used was support vector machine from R's kernlab package

--- 

## Example for using the predictive model

```{r}
# Load shiny and kernlab packages
library(shiny)
library(kernlab)
```

```{r}
# Load the predictive model from a file
model <- load("apartment_prices_model_svm.rda")
```

```{r}
# Set the apartment attributes
data <- data.frame( Zip=100, Rooms=3, m2=50, Year=2010, Floor=3, Elevator=1, Condition=2)
```

```{r}
# Generate a prediction for the apartment price
predict(get(model), data, type = "decision")[[1]]
```




